Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-15 paper/paper.tex
Added more to the references section

\documentclass[10pt]{article}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{amsmath, amsthm, amssymb, amsrefs}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{breqn}
\usepackage{alltt}

@@

To further explain the algorithm behind this method, first let us describe how the object would be represented.  The method used is most similar to the second representation of objects discussed previously, as spheres and cylinders in a graph layout.  Each object would consist of a list of nodes or spheres $W$, a list of edges or cylinders $E$, and a radius $r$.  The nodes in $W$ are described using 3-tuples of floating point numbers, representing their location in Cartesian 3-space, and the edges in $E$ are represented by 2-tuples of indexes, referencing the two nodes in $W$.  The algorithm iterates over the nodes in $W$, creating spheres of radius $r$.  Then, it iterates over the edges in $E$, and for each edge $e$ creates cylinders with radius $r$ and endpoints centered on the two nodes in $W$ indexed by $e$.  This is done using pyOpenGL's

@@

\end{appendices}

\begin{bibdiv}
 \begin{biblist}
  \bib{Dasgupta}{book}{
   title={Algorithms},
   author={Dasgupta, Sanjoy},
   author={Papadimitriou, Christos},
   author={Vazirani, Umesh},
   publisher={McGraw-Hill Education},
   address={New York},
   year={2006}  
  }

  \bib{pyOpenGL}{webpage}{
   title={PyOpenGL Documentation},
   url={http://pyopengl.sourceforge.net/documentation/},
   accessdate={October 2015}
  }
 \end{biblist}
\end{bibdiv}

>>>>

\documentclass[10pt]{article}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{amsmath, amsthm, amssymb, amsrefs}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{breqn}
\usepackage{alltt}
\renewcommand{\baselinestretch}{1.5}

@@

To further explain the algorithm behind this method, first let us describe how the object would be represented.  The method used is most similar to the second representation of objects discussed previously, as spheres and cylinders in a graph layout.  Each object would consist of a list of nodes or spheres $W$, a list of edges or cylinders $E$, and a radius $r$.  The nodes in $W$ are described using 3-tuples of floating point numbers, representing their location in Cartesian 3-space, and the edges in $E$ are represented by 2-tuples of indexes, referencing the two nodes in $W$.  The algorithm iterates over the nodes in $W$, creating spheres of radius $r$.  Then, it iterates over the edges in $E$, and for each edge $e$ creates cylinders with radius $r$ and endpoints centered on the two nodes in $W$ indexed by $e$.  This is done using pyOpenGL's \texttt{gluSphere()} to draw spheres and \texttt{gluCylinder()} to draw cylinders.  For more information on the programming in this implementation, see \texttt{renderObject.py}.\cite{gitrepo}

@@

\end{appendices}
% ftp://ftp.ams.org/ams/amsrefs/amsrdoc.pdf for amsrefs documentation
\begin{bibdiv}
 \begin{biblist}
  \bib{Dasgupta}{book}{
   title={Algorithms},
   author={Dasgupta, Sanjoy},
   author={Papadimitriou, Christos},
   author={Vazirani, Umesh},
   publisher={McGraw-Hill Education},
   address={New York},
   year={2006}  
  }
  \bib{pyOpenGL}{webpage}{
   title={PyOpenGL Documentation},
   url={http://pyopengl.sourceforge.net/documentation/},
   accessdate={2015-10}
  }
  \bib{gitrepo}{webpage}{
   title={Genetic Algorithms for Shadow Sculptures},
   author={Chris Chappell},
   author={James Hoctor},
   url={https://github.com/chappc/Math-Senior-Research},
   accessdate={2015-12}
  }
  \bib{cylindermagic}{webpage}{
   title={Rendering a Cylinder Between Two Points in OpenGL},
   author={Parris, Joel},
   url={http://lifeofaprogrammergeek.blogspot.com/2008/07/rendering-cylinder-between-two-points.html},
   accessdate={2015-10}
  }
 \end{biblist}

\end{bibdiv}
